### 2023-03-02 paper/content.tex

\noindent
in which $r = \sqrt{(x - x_c)^2 + (y - y_c)^2 + (z - z_c)^2}$ is the Cartesian
distance between the observation point $(x, y, z)$ and the source $(x_c, y_c,
z_c)$ and $\mu_0$ is the vacuum magnetic permeability. Most magnetic
microscopes provide measurements of only the vertical component $b_z$, which
can be isolated from Equation~\ref{eq_vector_dipole_field} as

@@

In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies and sensors limitations. This noise added to the observed data vector affects the solution of the estimated parameter vector $\mathbf{m}$, regardless of the method used. Assuming that the noise in the observed data measure is independent and of variance ${\sigma_0}^2$, the latter given by (i) the squared standard deviation used in synthetic cases (e.g., pseudo-random normal distributions) or (ii) the sensor limitations for real samples. Nevertheless, if the sample's variance is not known, one can typically estimate it by using the \emph{$\chi^2$} statistic, \citep[Eq.~\ref{chi_square},][]{Aster2019}, which depends on the residual sum of squares and the degrees of freedom (\emph{v}), the latter being the difference between the number of observed data points (N) and the parameters (m).

@@

It is relevant to highlight that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters. \cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}). The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data. On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data. Some authors \citep[e.g.,][]{Myre2019, CortesOrtuno2021, Lima2009} use another approach for the evaluation of the predicted model, called signal-to-noise ratio (SNR, Eq.~\ref{SNR}). SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor. The higher the SNR (in decibels) values the better it will be the fit of the predicted model. For a signal to be “visible”,  \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise. Thus, both $R^2$ and SNR techniques are appropriate to be used as a criteria filtering for reliability for dipolar inversions.

>>>>

\noindent
in which $r = \sqrt{(x - x_c)^2 + (y - y_c)^2 + (z - z_c)^2}$ is the Cartesian distance between the observation point $(x, y, z)$ and the source $(x_c, y_c, z_c)$ and $\mu_0$ is the vacuum magnetic permeability. Most magnetic microscopes provide measurements of only the vertical component $b_z$, which can be isolated from Equation~\ref{eq_vector_dipole_field} as shown in Equation~\ref{eq_dipole_bz}, which is a similar approach to the uniform model proposed by \cite{Weiss2007}.

@@

In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies, and sensor limitations. This noise added to the observed data vector affects the solution of the estimated parameter vector $\mathbf{m}$, regardless of the method used. Assuming that the noise in the observed data measure is independent and of variance ${\sigma_0}^2$, the latter given by (i) the squared standard deviation used in synthetic cases (e.g., pseudo-random normal distributions) or (ii) the sensor limitations for real samples. Nevertheless, if the sample's variance is not known, one can typically estimate it by using the \emph{$\chi^2$} statistic, \citep[Eq.~\ref{chi_square},][]{Aster2019}, which depends on the residual sum of squares and the degrees of freedom (\emph{v}), the latter being the difference between the number of observed data points (N) and the parameters (m).

@@

It is relevant to highlight that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters. \cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}). The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data. On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data. Some authors \citep[e.g.,][]{Myre2019, CortesOrtuno2021, Lima2009} use another approach for the evaluation of the predicted model, called signal-to-noise ratio (SNR, Eq.~\ref{SNR}). SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor. The higher the SNR (in decibels) values the better it will be the fit of the predicted model. For a signal to be “visible”,  \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise. Thus, both $R^2$ and SNR techniques are appropriate to be used as criteria filtering for reliability for dipolar inversions.
